¿La manzana cae lejos del árbol? Incidencia de la socialización familiar y

### 2021-05-28 paper.Rmd
Ediciones de texto y actualización de html

```{r include=FALSE, results='asis'}
pacman::p_load(summarytools,haven,sjPlot,dplyr,htmlwidgets, webshot)
st_css()
st_options(lang = "es",
           footnote = NA,
           bootstrap.css = F,
           custom.css = "input/css/dfsummary.css")
load(file = "input/data/proc/data.RData")
basereg <- data %>% select(formal,
                           disruptivo,
                           nodisruptivo,
                           act_marcha,
                           voto_apod,
                           educ_apod,
                           pad_libros,
                           conversacion,
                           apertura,
                           civico,
                           sexo,
                           dependencia) %>% na.omit(basereg)
str(apertura)

>>>>

```{r include=FALSE, results='asis'}
pacman::p_load(summarytools,haven,sjPlot,dplyr,htmlwidgets, webshot)
st_css()
st_options(lang = "es",
           footnote = NA,
           bootstrap.css = F,
           custom.css = "input/css/dfsummary.css")
load(file = "input/data/proc/data.RData")
basereg <- data %>% select(formal,
                           disruptivo,
                           nodisruptivo,
                           act_marcha,
                           voto_apod,
                           educ_apod,
                           pad_libros,
                           conversacion,
                           apertura,
                           civico,
                           sexo,
                           dependencia) %>% na.omit(basereg)
